Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2015-02-19 parts/intro.tex
last ref & remove last TODO

The approach used in this paper
consists in considering a broader class of models,
that we call Asynchronous Automata Network,
and that allows to naturally model these cooperations
by defining several requisites for a transition.
Moreover, such automata networks are still compatible with the notion of priority,
that can also be used to model different reaction rates in the model.
Asynchronous Automata Networks
(and, a fortiori, their restriction, the Process Hitting framework)
can be considered as a subset of Communicating Finite State Machines
or safe Petri Nets.
%or Synchronous Automata Networks,
%is inspired from the $\pi$-calculus,
Our work is thus related to such semantic ramifications
of extending traditional process algebras with the concept of priority
that allows for some transitions to be given precedence over others.
We focus here on static priorities that allow to model
time constraints such as reaction rates or delays between regulations,
but can also model preemptions between evolution branches.

>>>>

The approach used in this paper
consists in considering a broader class of models,
that we call Asynchronous Automata Network,
and that allows to naturally model these cooperations
by defining several requisites for a transition.
Moreover, such automata networks are still compatible with the notion of priority,
that can also be used to model different reaction rates in the model.
Asynchronous Automata Networks
(and, a fortiori, their restriction, the Process Hitting framework)
can be considered as a subset of Communicating Finite State Machines
or safe Petri Nets~\cite{PMR-PetriNets}.
%or Synchronous Automata Networks,
%is inspired from the $\pi$-calculus,
Our work is thus related to such semantic ramifications
of extending traditional process algebras with the concept of priority
that allows for some transitions to be given precedence over others.
We focus here on static priorities that allow to model
time constraints such as reaction rates or delays between regulations,
but can also model preemptions between evolution branches.
